Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-26 code-tests.tex
Tossed some ideas into the conclusions section.  Made a couple of small tweaks in the test problem section.
working on test problems.
working on test problems, adding a couple of figures.
updating code tests.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Double mach reflection}
\label{sec.tests.doublemach}
\red{(Brian)}
Problem type 4.  This is one of Alexei's test problems.  Tests
boundary conditions in hydro.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sedov Explosion}
\label{sec.tests.sedov}
\red{(Elizabeth)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Zel`Dovich Pancake}
\label{sec.tests.pancake}
\red{(Brian)}
Problem type 20, unigrid and AMR both.  Tests gravity + hydro.

@@

\subsubsection{Representative thermal conduction test}
\label{sec.tests.conduct}
\red{(Brian)}
One test for the thermal conduction (maybe 1 for isotropic, 1 for
anisotropic).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Double mach reflection}
\label{sec.tests.doublemach}
\red{(Brian)}

The double mach reflection test is a classic test of hydrodynamical
algorithms, and was originally described in
\citet{1984JCoPh..54..115W} \citep[and more recently in][]{2008ApJS..178..137S}.

Problem type 4.  This is one of Alexei's test problems.  Tests
boundary conditions in hydro.  See Figure~\ref{fig.doublemach}.

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/DoubleMachTest.eps}
\caption{Double mach test.}
\label{fig.doublemach}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sedov Explosion}
\label{sec.tests.sedov}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Zel`Dovich Pancake}
\label{sec.tests.pancake}
\red{(Brian)}
Problem type 20, unigrid and AMR both.  Tests gravity + hydro.  Figure~\ref{fig.pancake}.

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/AMRZeldovichPancake.eps}
\caption{Zel`Dovich Pancake test.}
\label{fig.pancake}
\end{center}
\end{figure}

@@

\subsubsection{Representative thermal conduction test}
\label{sec.tests.conduct}
\red{(Brian)}
One test for the thermal conduction (maybe 1 for isotropic, 1 for
anisotropic).  Figure~\ref{fig.conduct}.

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{figures/iso_conduction_final_output.eps}
\includegraphics[width=0.4\textwidth]{figures/aniso_conduction_final_output.eps}
\caption{Temperature blah blah.  Conduction tests!}
\label{fig.conduct}
\end{center}
\end{figure}
